\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{CV - Sagiv Malihi \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
King David Ave. 23/8,       & {\it Cellular:}  052-6087182 \\
Tel-Aviv           & {\it E-mail:}  sagivmalihi@gmail.com \\
\end{tabular}

\section{\sc Education}
{\bf Hebrew University}, Jerusalem, Israel \hfill {\bf 2005 - 2008} \\
\vspace*{-.1in}
\begin{list1}
\item[] B.Sc., Mathematics
\item[] Included in dean's list (2006, 2008) and received dean's award (2007)
\item[] Final Average - 96.6
\item[] Participated in a research project under supervision of prof. Ofer Biham - \\ 
        wrote a simulation for particle interactions on interstellar dust grains 
        and used it to study models for $H_2$ creation in the interstellar medium.
\end{list1}

{\bf ``Haman Talpiot - Aham'' Course}, IDF \hfill {\bf August 2000 - February 2001}\\
\vspace*{-.1in}
\begin{list1}
\item[] University-level education in applied mathematics (Statistics/Probability Theory and Algebra)
\item[] Also - selected subjects in computer-science (Algorithms/Data Structures) and programming skills (mostly in C/C++/Python)
\end{list1}

{\bf Galili High School}, Kfar-Saba, Israel \hfill {\bf 1997 - 2000}\\
\vspace*{-.1in}
\begin{list1}
\item[] Graduated with honors, 5 point bagrut in Computer-Science, Physics, and Computer-Graphics
\end{list1}


\section{\sc Professional Experience}
{\bf IBM - XIV}
%\vspace*{-.05in}
{\em Software Developer} \hfill {\bf 2009 - Present} 
\begin{list1}
\item[] Storage-related software development. Mostly in Python
\end{list1}

{\bf Klapka.co.il}
%\vspace*{-.1in}
{\em Web development and System Administration} \hfill {\bf 2008} 
\begin{list1}
\item[] Django \& Python based website, co-developed with two of my friends, mostly as a hobby.
\end{list1}

{\bf TACT - Software Experts}
%\vspace*{-.1in}
{\em Information Security Research} \hfill {\bf 2006 - 2009}
\begin{list1}
\item[] Assigned to a classified project at IDF intelligence unit
\end{list1}

{\bf IDF - Intelligence Corps Technological Unit}
%\vspace*{-.1in}

{\em Information Security Research} \hfill {\bf 2001-2004}
\begin{list1}
\item[] Low-level programming in embedded systems.
\item[] Network security research, and embedded security research.
\end{list1}

%\vspace{-.1cm}
{\em R\&D} \hfill {\bf 2001-2004}
\begin{list1}
\item[] Mathematical research.
\item[] Algorithms development, Algorithmical and low-level optimizations of software (C \& C++)
\item[] Development of a variety of research tools written in python.
\item[] Developed some parallel code in a massively paralleled environment (C)
\end{list1}

\section{\sc Skills} 
\begin{list2}
\item Expert in Python (also has experience in embedding and extending python with native code)
\item Experience in web development using django
\item Thorough knowledge of C/C++
\item Intimately familiar with the world of computer security
\item Experience in Assembly programming (also for ARM/PowerPC/MIPS)
\item Experience in developing under Unix/Linux operating systems, and also under windows.
\item Scripting (perl / unix shells (bash/tcsh) / python)
\item Familiar with many of the popular networking protocols (TCP/IP, HTTP, SNMP \ldots)
\item Highly motivated self-learner
% \item Proficient in \LaTeX
\end{list2}

\end{resume}
\end{document}




